---
title: "Grabbing & Prepping Data"
description: |
  Collecting is half the fun? 
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

# Building the Data
I used Dungeon.Report to grab and build data for this project. While the information Dungeon.Report collects is limited, it does provide more than enough context to help out this analysis. 

You can access the raw data collection in this Google Sheet: https://docs.google.com/spreadsheets/d/17D0gnlrt2qsdmKzsdK4GrphMNyzbp9VJIPYhcHtgBAY/edit#gid=1672282834

# Loading & Prepping for Analysis
We're going to use R for our analysis, which will let us read the data from Google Sheets, process that for analysis, prepare any models or statistical tests, and make some pretty charts. 

Let's start by loading in some helpful packages:

```{r, echo=TRUE, warning=FALSE,message=FALSE}

library(googlesheets4)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(DT)
library(lubridate)

```

Now let's grab the data from Google Sheets. We're creating two dataframes here: `runs` for data about individual dungeon attempts and `gsums` for Guardian-specific data.

```{r, echo=TRUE}
runs <- read_sheet("https://docs.google.com/spreadsheets/d/17D0gnlrt2qsdmKzsdK4GrphMNyzbp9VJIPYhcHtgBAY/edit#gid=1672282834",range = "'PitRuns'!A:AF")

gsums <- read_sheet("https://docs.google.com/spreadsheets/d/17D0gnlrt2qsdmKzsdK4GrphMNyzbp9VJIPYhcHtgBAY/edit#gid=1620985665",range = "'PlayerSummary'!A:G")

```

Let's inspect `runs` first. We can definitely see some issues that need to be addressed, but nothing too complicated. 

```{r}
datatable(runs,options=list(pageLength = 5),class='display')
```



Now `gsums` needs a bit more work, but that should be sorted out at the source (Google Sheets) since this is summarized data. Let's not worry about doing those transformations here though.

```{r}
datatable(gsums,options=list(),class='display')
```

