---
title: "The Joe Time Save"
description: |
  Or how he runs those caves - oh my! 
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

# Site reference
# https://www.andreashandel.com/posts/distill-github-website/

```

# The Hypothesis
Why are we here? Simple. I want to know if creepmyrtle's approach to The Tunnels encounter in the Pit of Heresy provides a statistically significant time-saving compared to other Guardians in my clan, Three Days of Sorrow.

Given the great resource of Dungeon.Report, we can quickly access and build datasets to perform this analysis and truly isolate any effect. Check out the 'Data Collection' page for more information on how I grabbed data for this project.

# The Data
We're going to use R for our analysis, which will let us read the data from Google Sheets, process that for analysis, prepare any models or statistical tests, and make some pretty charts. 

Let's start by loading in some helpful packages:

```{r, echo=TRUE, warning=FALSE,message=FALSE}

library(googlesheets4)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(DT)
library(lubridate)

```

Now let's grab the data from Google Sheets. We're creating two dataframes here: `runs` for data about individual dungeon attempts and `gsums` for Guardian-specific data.

```{r, echo=TRUE}
runs <- read_sheet("https://docs.google.com/spreadsheets/d/17D0gnlrt2qsdmKzsdK4GrphMNyzbp9VJIPYhcHtgBAY/edit#gid=1672282834",range = "'PitRuns'!A:AF")

gsums <- read_sheet("https://docs.google.com/spreadsheets/d/17D0gnlrt2qsdmKzsdK4GrphMNyzbp9VJIPYhcHtgBAY/edit#gid=1620985665",range = "'PlayerSummary'!A:G")

```

Let's inspect `runs` first: 

```{r}
datatable(runs,options=list(pageLength = 5),class='display')
```

We definitely need to tidy this data up a bit. So we'll do that by cleaning up the date field, 

Now `gsums`:

```{r}
datatable(gsums,options=list(),class='display')
```

